Dominance Regions for Affine Cluster Algebras

### 2022-06-21 affine_dominance.tex
Small correction

  \begin{lemma}
    For any imaginary $\bfg$-vector $\lambda\in\ZZ^n$ and any source or sink adapted sequence of mutations, the coefficient part of  
    \[E^{t_{r-1}}_{\ell,\varepsilon_{r-1}} \cdots E^{t_{r-\ell}}_{1,\varepsilon_{r-\ell}} E^{t_{ns-1}}_{n,\varepsilon_{ns-1}} \cdots E^{t_1}_{2,\varepsilon_1} E^{t_0}_{1,\varepsilon_0} \lambda\]
    stabilizes after the first $n$ mutations.
  \end{lemma}
  \begin{proof}
    If the sequence is sink adapted, the coefficient part is always just zero.

>>>>

  For a $\bfg$-vector $\lambda\in\ZZ^n$, write $\tilde\lambda\in\ZZ^{2n}$ for its extension by zeros.
  \begin{lemma}
    For any imaginary $\bfg$-vector $\lambda\in\ZZ^n$ and any source or sink adapted sequence of mutations, the coefficient part of
    \[E^{t_{r-1}}_{\ell,\varepsilon_{r-1}} \cdots E^{t_{r-\ell}}_{1,\varepsilon_{r-\ell}} E^{t_{ns-1}}_{n,\varepsilon_{ns-1}} \cdots E^{t_1}_{2,\varepsilon_1} E^{t_0}_{1,\varepsilon_0} \tilde\lambda\]
    stabilizes after the first $n$ mutations.
  \end{lemma}
  \begin{proof}
    If the sequence is sink adapted, the coefficient part is always just zero.
